---
title: "isZeroInformative"
output: html_document
---

```{r}
library(here)
library(dplyr)
library(tidyr)
library(purrr)
library(tibble)
```

```{r, readin}
file_path <- here("Data", "Camila_Bedeutung", "data_prepared.csv")
cam_bed <- read.csv(file_path, sep = ";")

file_path <- here("Data", "Camila_Einheit", "data_prepared.csv")
cam_ein <- read.csv(file_path, sep = ";")

file_path <- here("Data", "Nebrija_Bedeutung", "data_prepared.csv")
neb_bed <- read.csv(file_path, sep = ";")

file_path <- here("Data", "Nebrija_Einheit", "data_prepared.csv")
neb_ein <- read.csv(file_path, sep = ";")

file_path <- here("Data", "Code_Switching", "data_prepared_new.csv")
cs <- read.csv(file_path, sep = ";")

file_path <- here("Data", "Incluso", "data_prepared.csv")
inc <- read.csv(file_path, sep = ";")
```

```{r, make col.names equal}
inc <- inc %>%
  dplyr::rename(
    RRT    = SRT,
    RRT.WD = SRT.WD,
    condition = Kondition
  )

cs <- cs %>%
  dplyr::rename(
    nWords    = WORD_COUNT,
    nLetters = CHARACTER_COUNT,
    Topic = TOPIC,
    Participant = ID_PARTICIPANT,
    condition = CONDITION,
    nLetters.WD = CHARACTER_COUNT.WD
  )
```

```{r, make factors}
# pack your data frames
dfs <- list(
  cam_bed = cam_bed,
  cam_ein = cam_ein,
  neb_bed = neb_bed,
  neb_ein = neb_ein,
  cs      = cs,
  inc     = inc
)

make_factor_cols <- function(df) {
  # core IDs
  core <- c("Participant", "AOI", "Topic", "condition")

  # common extra grouping and design columns across your projects
  extras <- c(
    "speaker", "speaker_group", "participant_group", "group", "PARTICIPANT_GROUP", "Stimulus", 
    "meaning", "unit",
    "a", "b",
    "Themenblock", "Thema", "Themen", "List", "list"
  )

  cols <- intersect(c(core, extras), names(df))

  df %>%
    mutate(across(all_of(cols), ~ as.factor(.x)))
}

dfs <- imap(dfs, ~ make_factor_cols(.x))
```

```{r, make .WD integers}
dfs <- list(
  cam_bed = cam_bed,
  cam_ein = cam_ein,
  neb_bed = neb_bed,
  neb_ein = neb_ein,
  cs      = cs,
  inc     = inc
)

to_num_comma <- function(x) {
  if (is.factor(x)) x <- as.character(x)
  if (is.character(x)) x <- gsub(",", ".", x, fixed = TRUE)
  suppressWarnings(as.numeric(x))
}

cols_to_int <- c("FRT.WD", "RRT.WD", "TRT.WD", "nLetters.WD")

make_int_cols <- function(df) {
  cols <- intersect(cols_to_int, names(df))
  if (length(cols) == 0) return(df)

  df %>%
    mutate(across(
      all_of(cols),
      ~ as.integer(round(to_num_comma(.x)))
    ))
}

dfs <- imap(dfs, ~ make_int_cols(.x))
```


cs wurde nicht bereinigt, oder falsch. 
Oder AOI 2 ist nicht gesamter Text:
In descriptionReport wird whole critical Item beschrieben. Dabei summieren wir in der Outlier Definition (siehe Rmd cs: 1_descriptionReport_new.rmd) AOIs für "whole critical item".

cs wird neu gecleaned, wegen fehler in desc.rep. nötig (sie haben any.fast.reader nicht auf RRT überprüft)
```{r, cs neu cleanen}
# robust numeric parsing (handles comma decimals if they ever appear)
to_num <- function(x) {
  if (is.factor(x)) x <- as.character(x)
  if (is.character(x)) x <- gsub(",", ".", x, fixed = TRUE)
  suppressWarnings(as.numeric(x))
}

clean_cs_outliers <- function(cs,
                              thr_fast = 80,   # ms/word
                              thr_slow = 800   # ms/word
) {
  # 0) enforce required columns
  req <- c("TRIAL","Participant","Topic","condition","PARTICIPANT_GROUP",
           "AOI","nWords","TRT","FRT","RRT")
  miss <- setdiff(req, names(cs))
  if (length(miss) > 0) stop(paste("Missing columns:", paste(miss, collapse = ", ")), call. = FALSE)

  # 1) parse numeric columns (do NOT round before flagging outliers)
  cs2 <- cs %>%
    mutate(across(all_of(c("nWords","TRT","FRT","RRT")), to_num))

  # 2) build "whole critical item" per TRIAL by summing over AOIs
  whole_ci <- cs2 %>%
    group_by(TRIAL) %>%
    summarise(
      Participant = first(Participant),
      Topic = first(Topic),
      condition = first(condition),
      PARTICIPANT_GROUP = first(PARTICIPANT_GROUP),
      # sums over AOIs
      TRT_sum = sum(TRT, na.rm = TRUE),
      FRT_sum = sum(FRT, na.rm = TRUE),
      RRT_sum = sum(RRT, na.rm = TRUE),
      nWords_sum = sum(nWords, na.rm = TRUE),
      n_AOI = n_distinct(AOI),
      .groups = "drop"
    ) %>%
    mutate(
      TRT.WD = TRT_sum / nWords_sum,
      FRT.WD = FRT_sum / nWords_sum,
      RRT.WD = RRT_sum / nWords_sum,
      # outlier rules on whole critical item (per word)
      out_first_skip  = is.finite(FRT.WD) & FRT.WD == 0,
      out_fast_reader = is.finite(FRT.WD) & is.finite(RRT.WD) & FRT.WD < thr_fast & RRT.WD < thr_fast,
      out_slow_reader = is.finite(TRT.WD) & TRT.WD > thr_slow,
      any_outlier = out_first_skip | out_fast_reader | out_slow_reader
    )

  out_trials <- whole_ci %>%
    filter(any_outlier) %>%
    pull(TRIAL) %>%
    unique()

  # 3) delete full trials from the original AOI-level data
  cs_clean <- cs2 %>%
    filter(!(TRIAL %in% out_trials))

  # 4) small summary you can print in the report
  summary <- whole_ci %>%
    summarise(
      n_trials = n(),
      n_out_trials = sum(any_outlier),
      n_first_skip = sum(out_first_skip),
      n_fast_reader = sum(out_fast_reader),
      n_slow_reader = sum(out_slow_reader),
      .groups = "drop"
    )

  list(
    cs_clean = cs_clean,
    whole_ci = whole_ci,
    out_trials = out_trials,
    summary = summary
  )
}

# run it
res_cs <- clean_cs_outliers(cs)

res_cs$summary
res_cs$whole_ci %>%
  filter(any_outlier) %>%
  select(TRIAL, Participant, Topic, condition, PARTICIPANT_GROUP,
         nWords_sum, FRT.WD, RRT.WD, TRT.WD,
         out_first_skip, out_fast_reader, out_slow_reader)
```

ein Trial fällt raus.
```{r, cs überschreiben}
cs <- res_cs$cs_clean
```

Nebrija fixed
```{r}
neb_ein <- neb_ein %>%
  mutate(
    condition_chr = as.character(condition),
    AOI_num = as.integer(as.character(AOI)),
    AOI_num = ifelse(
      Topic == "S2" &
        grepl("_CU$", condition_chr) &
        AOI_num == 4 &
        nLetters == 5,
      3,
      AOI_num
    ),
    AOI = factor(AOI_num)
  ) %>%
  select(-condition_chr, -AOI_num)
```

Inc Fixed, AOI AT mit nLetters = 5 gelöscht, sind exakte kopien für AOI F.
```{r}
# remove the duplicated AT rows that are exact copies of F (Topic T9, condition c1a1, nLetters=5)
inc <- inc %>%
  anti_join(
    inc %>%
      filter(Topic == "T9", condition == "c1a1", AOI == "AT", nLetters == 5) %>%
      select(Participant, Topic, condition, AOI, nWords, nLetters, FRT, RRT, TRT),
    by = c("Participant","Topic","condition","AOI","nWords","nLetters","FRT","RRT","TRT")
  )
```



Is Zero Informative? If yes: think twice about modeling > 0. Otherwise interpretation changes to:
For AOIs which were fixated in the First Pass: 

We check for: TRT, FRT & RRT.

TRT:
```{r}
dfs_raw <- list(
  cam_bed = cam_bed,
  cam_ein = cam_ein,
  neb_bed = neb_bed,
  neb_ein = neb_ein,
  cs      = cs,
  inc     = inc
)

as_numeric_safe <- function(x) {
  if (is.factor(x)) x <- as.character(x)
  if (is.character(x)) x <- gsub(",", ".", x, fixed = TRUE)
  suppressWarnings(as.numeric(x))
}

skip_return_summary <- function(df, exp_name) {
  FRTn <- as_numeric_safe(df$FRT)
  RRTn <- if ("RRT" %in% names(df)) as_numeric_safe(df$RRT) else rep(NA_real_, nrow(df))
  TRTN <- if ("TRT" %in% names(df)) as_numeric_safe(df$TRT) else rep(NA_real_, nrow(df))

  trt0 <- is.finite(TRTN) & TRTN == 0
  trtpos <- is.finite(TRTN) & TRTN > 0

  frt0 <- is.finite(FRTn) & FRTn == 0
  frtpos <- is.finite(FRTn) & FRTn > 0

  rrt0 <- is.finite(RRTn) & RRTn == 0
  rrtpos <- is.finite(RRTn) & RRTn > 0

  tibble(
    Experiment = exp_name,
    n_rows = nrow(df),

    # never fixated
    n_TRT0 = sum(trt0, na.rm = TRUE),
    prop_TRT0 = mean(trt0, na.rm = TRUE),

    # skip then return: no first-pass, but some later fixation (TRT>0)
    n_FRT0_TRTpos = sum(frt0 & trtpos, na.rm = TRUE),
    prop_FRT0_TRTpos = mean(frt0 & trtpos, na.rm = TRUE),

    # among "at risk" rows (TRT>0): how often is RRT positive?
    n_TRTpos = sum(trtpos, na.rm = TRUE),
    prop_RRTpos_given_TRTpos = ifelse(sum(trtpos, na.rm = TRUE) == 0, NA_real_,
                                      sum(rrtpos & trtpos, na.rm = TRUE) / sum(trtpos, na.rm = TRUE)),

    # optional: among TRT>0, how often is FRT==0 (skip first pass)
    prop_FRT0_given_TRTpos = ifelse(sum(trtpos, na.rm = TRUE) == 0, NA_real_,
                                    sum(frt0 & trtpos, na.rm = TRUE) / sum(trtpos, na.rm = TRUE))
  )
}

skip_return_table <- imap_dfr(dfs_raw, ~ skip_return_summary(.x, .y))
skip_return_table
```
wir sehen: keine FRT = 0 ohne TRT = 0, also reicht TRT analyse aus. 

```{r}
dfs_raw <- list(
  cam_bed = cam_bed,
  cam_ein = cam_ein,
  neb_bed = neb_bed,
  neb_ein = neb_ein,
  cs      = cs,
  inc     = inc
)

as_numeric_safe <- function(x) {
  if (is.factor(x)) x <- as.character(x)
  if (is.character(x)) x <- gsub(",", ".", x, fixed = TRUE)
  suppressWarnings(as.numeric(x))
}

trt0_len_table <- function(df) {
  if (!("TRT" %in% names(df))) return(NULL)

  trt_num <- as_numeric_safe(df$TRT)

  df %>%
    mutate(TRT_num = trt_num) %>%
    filter(is.finite(TRT_num) & TRT_num == 0) %>%
    count(AOI, nWords, nLetters, name = "n_trt0") %>%
    arrange(desc(n_trt0), AOI, nWords, nLetters)
}

trt0_len_by_exp <- imap(dfs_raw, ~ trt0_len_table(.x))

print_trt0_len <- function(exp_name) {
  cat("\n============================\n")
  cat("Experiment:", exp_name, "\n")
  cat("============================\n")
  x <- trt0_len_by_exp[[exp_name]]
  if (is.null(x)) {
    cat("TRT not available in this experiment\n")
  } else {
    print(x)
  }
}

print_trt0_len("cam_bed")
print_trt0_len("cam_ein")
print_trt0_len("neb_bed")
print_trt0_len("neb_ein")
print_trt0_len("cs")
print_trt0_len("inc")
```

```{r, TRT helpers}
# Block 1/4: Setup + helpers (TRT==0)

dfs_raw <- list(
  cam_bed = cam_bed,
  cam_ein = cam_ein,
  neb_bed = neb_bed,
  neb_ein = neb_ein,
  cs      = cs,
  inc     = inc
)

as_numeric_safe <- function(x) {
  if (is.factor(x)) x <- as.character(x)
  if (is.character(x)) x <- gsub(",", ".", x, fixed = TRUE)
  suppressWarnings(as.numeric(x))
}

add_trt0 <- function(df) {
  if (!("TRT" %in% names(df))) {
    return(df %>% mutate(trt0 = NA))
  }
  trt_num <- as_numeric_safe(df$TRT)
  df %>% mutate(trt0 = is.finite(trt_num) & trt_num == 0)
}

prop_table <- function(df, var) {
  df %>%
    group_by(.data[[var]]) %>%
    summarise(
      n = n(),
      n_trt0 = sum(trt0, na.rm = TRUE),
      prop_trt0 = mean(trt0, na.rm = TRUE),
      .groups = "drop"
    )
}

overall_table <- function(df, exp_name) {
  tibble(
    Experiment = exp_name,
    n = nrow(df),
    n_trt0 = sum(df$trt0, na.rm = TRUE),
    prop_trt0 = mean(df$trt0, na.rm = TRUE)
  )
}

# Nebrija: speaker is prefix of condition (H/E/N)
add_neb_speaker <- function(df) {
  df %>%
    mutate(
      .cond_chr = as.character(condition),
      speaker = factor(sub("_.*$", "", .cond_chr))
    ) %>%
    select(-.cond_chr)
}

# cs: participant group column name
get_cs_group_col <- function(df) {
  intersect(c("PARTICIPANT_GROUP", "participant_group", "group"), names(df))[1]
}
```

```{r, Proportion der 0er insgesamt}
# Block 2/4: Proportion der 0er insgesamt (TRT==0), alle Experimente

trt0_overall <- imap_dfr(dfs_raw, function(df, nm) {
  df1 <- add_trt0(df)
  overall_table(df1, nm)
})

trt0_overall
```

```{r, Proportion der 0er nach Condition und nach AOI}
# Block 3/4: Proportion der 0er nach Condition und nach AOI, alle Experimente

trt0_by_condition <- imap(dfs_raw, function(df, nm) {
  df1 <- add_trt0(df)
  prop_table(df1, "condition")
})

trt0_by_AOI <- imap(dfs_raw, function(df, nm) {
  df1 <- add_trt0(df)
  prop_table(df1, "AOI")
})

print_trt0_cond_aoi <- function(exp_name) {
  cat("\n============================\n")
  cat("Experiment:", exp_name, "\n")
  cat("============================\n")

  cat("\nTRT==0 nach Condition\n")
  print(trt0_by_condition[[exp_name]])
}

print_trt0_cond_aoi("cam_bed")
print_trt0_cond_aoi("cam_ein")
print_trt0_cond_aoi("neb_bed")
print_trt0_cond_aoi("neb_ein")
print_trt0_cond_aoi("cs")
print_trt0_cond_aoi("inc")
```

```{r}
print_trt0_cond_aoi <- function(exp_name) {
  cat("\n============================\n")
  cat("Experiment:", exp_name, "\n")
  cat("============================\n")


  cat("\nTRT==0 nach AOI\n")
  print(trt0_by_AOI[[exp_name]])
}

print_trt0_cond_aoi("cam_bed")
print_trt0_cond_aoi("cam_ein")
print_trt0_cond_aoi("neb_bed")
print_trt0_cond_aoi("neb_ein")
print_trt0_cond_aoi("cs")
print_trt0_cond_aoi("inc")
```

```{r}
# Block 4/4: Proportion der 0er nach Speaker Groups, nur Nebrija und cs

# Nebrija
trt0_neb_bed_speaker <- {
  df1 <- add_neb_speaker(add_trt0(neb_bed))
  prop_table(df1, "speaker")
}

trt0_neb_ein_speaker <- {
  df1 <- add_neb_speaker(add_trt0(neb_ein))
  prop_table(df1, "speaker")
}

# cs
cs_group_col <- get_cs_group_col(cs)
stopifnot(!is.na(cs_group_col))

trt0_cs_group <- {
  df1 <- add_trt0(cs) %>% mutate(participant_group = factor(.data[[cs_group_col]]))
  prop_table(df1, "participant_group")
}

cat("\n============================\nExperiment: neb_bed\n============================\n")
print(trt0_neb_bed_speaker)

cat("\n============================\nExperiment: neb_ein\n============================\n")
print(trt0_neb_ein_speaker)

cat("\n============================\nExperiment: cs\n============================\n")
print(trt0_cs_group)
```

```{r}
# TRT==0: Condition x Topic (Nebrija: split condition into speaker + treatment, use treatment)
library(dplyr)
library(purrr)

dfs_raw <- list(
  cam_bed = cam_bed,
  cam_ein = cam_ein,
  neb_bed = neb_bed,
  neb_ein = neb_ein,
  cs      = cs,
  inc     = inc
)

as_numeric_safe <- function(x) {
  if (is.factor(x)) x <- as.character(x)
  if (is.character(x)) x <- gsub(",", ".", x, fixed = TRUE)
  suppressWarnings(as.numeric(x))
}

add_neb_treatment <- function(df) {
  df %>%
    mutate(
      .cond_chr = as.character(condition),
      speaker   = factor(sub("_.*$", "", .cond_chr)),
      treatment = factor(sub("^.*_", "", .cond_chr))
    ) %>%
    select(-.cond_chr)
}

trt0_cond_topic <- function(df, exp_name) {
  stopifnot("TRT" %in% names(df))
  trt_num <- as_numeric_safe(df$TRT)

  df1 <- df %>%
    mutate(TRT_num = trt_num,
           trt_valid = is.finite(TRT_num),
           trt0 = trt_valid & TRT_num == 0)

  # Nebrija: replace condition with treatment (suffix)
  if (exp_name %in% c("neb_bed", "neb_ein")) {
    df1 <- add_neb_treatment(df1) %>% mutate(condition2 = treatment)
    group_vars <- c("condition2", "Topic")
  } else {
    df1 <- df1 %>% mutate(condition2 = condition)
    group_vars <- c("condition2", "Topic")
  }

  df1 %>%
    group_by(across(all_of(group_vars))) %>%
    summarise(
      n = sum(trt_valid),
      n_0 = sum(trt0),
      prop_0 = ifelse(n == 0, NA_real_, n_0 / n),
      .groups = "drop"
    ) %>%
    rename(condition = condition2) #%>%
    #arrange(desc(prop_0), desc(n_0), Topic, condition)
}

trt0_cond_topic_by_exp <- imap(dfs_raw, ~ if (!("TRT" %in% names(.x))) NULL else trt0_cond_topic(.x, .y))

print_trt0_cond_topic <- function(exp_name) {
  cat("\n============================\n")
  cat("Experiment:", exp_name, "\n")
  cat("============================\n")
  x <- trt0_cond_topic_by_exp[[exp_name]]
  if (is.null(x)) cat("TRT not available\n") else print(x)
}

print_trt0_cond_topic("cam_bed")
print_trt0_cond_topic("cam_ein")
print_trt0_cond_topic("neb_bed")
print_trt0_cond_topic("neb_ein")
print_trt0_cond_topic("cs")
print_trt0_cond_topic("inc")
```


```{r}
dfs_raw <- list(
  cam_bed = cam_bed,
  cam_ein = cam_ein,
  neb_bed = neb_bed,
  neb_ein = neb_ein,
  cs      = cs,
  inc     = inc
)

as_numeric_safe <- function(x) {
  if (is.factor(x)) x <- as.character(x)
  if (is.character(x)) x <- gsub(",", ".", x, fixed = TRUE)
  suppressWarnings(as.numeric(x))
}

add_neb_treatment <- function(df) {
  df %>%
    mutate(
      .cond_chr = as.character(condition),
      treatment = factor(sub("^.*_", "", .cond_chr))
    ) %>%
    select(-.cond_chr)
}

trt0_aoi_cond_meanletters <- function(df, exp_name) {
  stopifnot("TRT" %in% names(df))

  trt_num <- as_numeric_safe(df$TRT)
  nl_num  <- if ("nLetters" %in% names(df)) as_numeric_safe(df$nLetters) else rep(NA_real_, nrow(df))

  df1 <- df %>%
    mutate(
      TRT_num = trt_num,
      nLetters_num = nl_num,
      trt_valid = is.finite(TRT_num),
      trt0 = trt_valid & TRT_num == 0
    )

  if (exp_name %in% c("neb_bed", "neb_ein")) {
    df1 <- add_neb_treatment(df1) %>% mutate(condition2 = treatment)
  } else {
    df1 <- df1 %>% mutate(condition2 = condition)
  }

  df1 %>%
    group_by(AOI, condition2) %>%
    summarise(
      n = sum(trt_valid),
      n_0 = sum(trt0),
      prop_0 = ifelse(n == 0, NA_real_, n_0 / n),
      mean_nLetters = mean(nLetters_num, na.rm = TRUE),
      min_nLetters = suppressWarnings(min(nLetters_num, na.rm = TRUE)),
      max_nLetters = suppressWarnings(max(nLetters_num, na.rm = TRUE)),
      .groups = "drop"
    ) %>%
    mutate(
      min_nLetters = ifelse(is.infinite(min_nLetters), NA_real_, min_nLetters),
      max_nLetters = ifelse(is.infinite(max_nLetters), NA_real_, max_nLetters)
    ) %>%
    rename(condition = condition2) %>%
    mutate(across(where(is.numeric), ~ round(.x, 2))) #%>%
    #arrange(desc(prop_0), desc(n_0), AOI, condition)
}

trt0_aoi_cond_by_exp <- imap(dfs_raw, ~ if (!("TRT" %in% names(.x))) NULL else trt0_aoi_cond_meanletters(.x, .y))

print_trt0_aoi_cond <- function(exp_name) {
  cat("\n============================\n")
  cat("Experiment:", exp_name, "\n")
  cat("============================\n")
  x <- trt0_aoi_cond_by_exp[[exp_name]]
  if (is.null(x)) cat("TRT not available\n") else print(x)
}

print_trt0_aoi_cond("cam_bed")
print_trt0_aoi_cond("cam_ein")
print_trt0_aoi_cond("neb_bed")
print_trt0_aoi_cond("neb_ein")
print_trt0_aoi_cond("cs")
print_trt0_aoi_cond("inc")
```


0s von Länge oder von condition verursacht
```{r}

dfs_raw <- list(
  cam_bed = cam_bed,
  cam_ein = cam_ein,
  neb_bed = neb_bed,
  neb_ein = neb_ein,
  cs      = cs,
  inc     = inc
)

as_numeric_safe <- function(x) {
  if (is.factor(x)) x <- as.character(x)
  if (is.character(x)) x <- gsub(",", ".", x, fixed = TRUE)
  suppressWarnings(as.numeric(x))
}

add_neb_treatment <- function(df) {
  df %>%
    mutate(.cond_chr = as.character(condition),
           condition2 = factor(sub("^.*_", "", .cond_chr))) %>%
    select(-.cond_chr)
}

length_by_condition <- function(df, exp_name) {
  nl <- as_numeric_safe(df$nLetters)
  df1 <- df %>% mutate(nLetters_num = nl)

  if (exp_name %in% c("neb_bed","neb_ein")) df1 <- add_neb_treatment(df1) else df1 <- df1 %>% mutate(condition2 = condition)

  df1 %>%
    group_by(condition2) %>%
    summarise(
      n = n(),
      mean_nLetters = mean(nLetters_num, na.rm = TRUE),
      sd_nLetters = sd(nLetters_num, na.rm = TRUE),
      min_nLetters = min(nLetters_num, na.rm = TRUE),
      max_nLetters = max(nLetters_num, na.rm = TRUE),
      .groups = "drop"
    ) %>%
    mutate(across(where(is.numeric), ~ round(.x, 2))) %>%
    rename(condition = condition2) %>%
    arrange(desc(mean_nLetters))
}

len_by_exp <- imap(dfs_raw, ~ length_by_condition(.x, .y))

print_len <- function(exp) {
  cat("\n============================\nExperiment:", exp, "\n============================\n")
  print(len_by_exp[[exp]])
}

print_len("cam_bed"); print_len("cam_ein"); print_len("neb_bed"); print_len("neb_ein"); print_len("cs"); print_len("inc")
```


```{r}

trt0_by_condition_within_lengthbins <- function(df, exp_name, n_bins = 5) {
  if (!("TRT" %in% names(df))) return(NULL)

  TRTN <- as_numeric_safe(df$TRT)
  nl <- as_numeric_safe(df$nLetters)

  df1 <- df %>%
    mutate(
      TRT_num = TRTN,
      trt_valid = is.finite(TRT_num),
      trt0 = trt_valid & TRT_num == 0,
      nLetters_num = nl
    ) %>%
    filter(!is.na(nLetters_num))

  if (exp_name %in% c("neb_bed","neb_ein")) df1 <- add_neb_treatment(df1) else df1 <- df1 %>% mutate(condition2 = condition)

  # Bins nach nLetters innerhalb des Experiments
  qs <- quantile(df1$nLetters_num, probs = seq(0, 1, length.out = n_bins + 1), na.rm = TRUE)
  qs <- unique(qs)
  if (length(qs) < 3) return(NULL)

  df1 <- df1 %>%
    mutate(len_bin = cut(nLetters_num, breaks = qs, include.lowest = TRUE, right = TRUE))

  # Zellrate: pro (condition, len_bin) Anteil TRT==0
  cell <- df1 %>%
    group_by(condition2, len_bin) %>%
    summarise(
      n = sum(trt_valid),
      n_0 = sum(trt0),
      prop_0 = ifelse(n == 0, NA_real_, n_0 / n),
      .groups = "drop"
    )

  # Standardisierung: gleiche Laengenverteilung fuer alle Conditions
  w <- df1 %>%
    group_by(len_bin) %>%
    summarise(w = n() / nrow(df1), .groups = "drop")

  # Replace the "std" part in check 2 with this renormalized version

std <- cell %>%
  left_join(w, by = "len_bin") %>%
  group_by(condition2) %>%
  summarise(
    std_prop_0 = {
      ww <- w
      pp <- prop_0
      denom <- sum(ww[!is.na(pp)])
      ifelse(denom == 0, NA_real_, sum(pp * ww, na.rm = TRUE) / denom)
    },
    .groups = "drop"
  )

  # Rohrate zum Vergleich
  raw <- df1 %>%
    group_by(condition2) %>%
    summarise(
      raw_prop_0 = mean(trt0, na.rm = TRUE),
      .groups = "drop"
    )

  list(
    cell_rates = cell %>% mutate(prop_0 = round(prop_0, 4)),
    raw_vs_std = raw %>% left_join(std, by = "condition2") %>%
      mutate(across(where(is.numeric), ~ round(.x, 4))) %>%
      rename(condition = condition2)
  )
}

out_bins <- imap(dfs_raw, ~ trt0_by_condition_within_lengthbins(.x, .y, n_bins = 5))

print_bins <- function(exp) {
  cat("\n============================\nExperiment:", exp, "\n============================\n")
  x <- out_bins[[exp]]
  if (is.null(x)) { cat("No output (maybe no TRT or too few distinct nLetters)\n"); return() }

  cat("\nRaw vs length-standardized prop(TRT==0)\n")
  print(x$raw_vs_std)

  cat("\nCell rates: condition x length-bin\n")
  print(x$cell_rates)
}

print_bins("cam_bed"); print_bins("cam_ein"); print_bins("neb_bed"); print_bins("neb_ein"); print_bins("cs"); print_bins("inc")
```
Ja, zero ist auch unabhängig von Länge ungleich zwischen conditions. 


